FAT-Pointer based range addresses

### 2024-05-21 papers/ISMM/FlexPointer/paper.tex
added new diagrams draw.io

In this context, the integration of huge pages into memory management 
strategies alongside capability-based addressing in architectures like 
CHERI offers a compelling synergy. By optimizing TLB utilization through the 
utilization of huge pages and leveraging the security features of capability-based addressing, 
significant performance improvements can be realized. This approach not only enhances 
system security but also accelerates memory access

@@

\subsection{Range creation}

\subsection{Fragmentation}

@@

>>>>

In this context, the integration of huge pages into memory management 
strategies alongside capability-based addressing in architectures like 
CHERI offers a compelling synergy. By optimizing TLB utilization through the 
utilization of huge pages and leveraging the security features of capability-based addressing, 
significant performance improvements can be realized. This approach not only enhances 
system security but also accelerates memory access.

@@

\subsection{Range creation}
Ranges of memory are created based on bounds encoded to the FAT-Pointer. 
The Chuck between the following bounds is physically contiguous.
This is done via the FreeBSD kernel Contig memory allocator.

\subsection{Fragmentation}
The problem with standard allocators which are physically contiguous
is that they are mostly on the

@@

\begin{table}[!ht]
  \centering
  \begin{tabular}{|l|l|l|l|l|}
  \hline
      \textbf{Metric name} & \textbf{type of graph} & \textbf{tool used} & \textbf{x axis} & \textbf{y axis} \\ \hline
      DTLB L1 read & line graph & Pmcstat & Time & DTLB L1 reads (each second) \\ \hline
      DTLB L2 read & line graph & Pmcstat & Time & DTLB L2 reads (each second) \\ \hline
      DTLB walk & line graph & Pmcstat & Time & DTLB Walks (each second) \\ \hline
      L1 cache miss & line graph & Pmcstat & Time & L1 cache miss (each second) \\ \hline
      Wall clock run time & bar graph & time & Benchmarks & Time \\ \hline
      Resident memory usage & line graph & ps with rss & Time & Memory in MB \\ \hline
      Speed ups & bar graph & time & Benchmarks & Time \\ \hline
  \end{tabular}
\end{table}
